Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2014-11-05 MS_revised.tex
added new ref 42 rabosky2014
added rabosky to list of refs

We contrasted these results with those obtained from analysing the data in
the software BAMM [@rabosky2014]. We found 
that the best model (best configuration) estimated 2 diversification shifts in
our MCC tree (posterior probability = 0.79) for the Ithomiini
 and Satyrini. Bayes factor (BF) values strongly 
favored this model in comparison with a constant rate model (no diversification
shifts, BF $>$ 1,884).

@@

42. Litman JR, Danforth BN, Eardley CD, Praz CJ (2011) Why do leafcutter
bees cut leaves? New insights into the early evolution of bees. P Roy
Soc B 278: 3593--3600.
doi:\href{http://dx.doi.org/10.1098/rspb.2011.0365}{10.1098/rspb.2011.0365}.

43. Ryberg M, Matheny PB (2012) Asynchronous origins of ectomycorrhizal
clades of Agaricales. P Roy Soc B 279: 2003--2011.
doi:\href{http://dx.doi.org/10.1098/rspb.2011.2428}{10.1098/rspb.2011.2428}.

44. Brown Jr. KS (1987) Chemistry at the Solanaceae/Ithomiinae
Interface. Ann Mo Bot Gard 74: 359--397.

45. Brower AVZ, Freitas AVL, Lee M-M, Silva-Brand{\~a}o KL, Whinnett A, et
al. (2006) Phylogenetic relationships among the Ithomiini (Lepidoptera:
Nymphalidae) inferred from one mitochondrial and two nuclear gene
regions. Syst Entomol 31: 288--301.
doi:\href{http://dx.doi.org/10.1111/j.1365-3113.2006.00321.x}{10.1111/j.1365-3113.2006.00321.x}.

46. {FitzJohn} RG, Maddison WP, Otto SP (2009) Estimating
trait-dependent speciation and extinction rates from incompletely
resolved phylogenies. Syst Biol 58: 595--611.
doi:\href{http://dx.doi.org/10.1093/sysbio/syp067}{10.1093/sysbio/syp067}.

47. Wheat CW, Vogel H, Wittstock U, Braby MB, Underwood D, et al. (2007)
The genetic basis of a plant-insect coevolutionary key innovation. P
Natl Acad Sci USA 104: 20427--20431.
doi:\href{http://dx.doi.org/10.1073/pnas.0706229104}{10.1073/pnas.0706229104}.

48. Li W, Schuler MA, Berenbaum MR (2003) Diversification of
furanocoumarin-metabolizing cytochrome P450 monooxygenases in two
papilionids: Specificity and substrate encounter rate. P Natl Acad Sci
USA 100: 14593--14598.
doi:\href{http://dx.doi.org/10.1073/pnas.1934643100}{10.1073/pnas.1934643100}.

49. Bell CD, Soltis DE, Soltis PS (2010) The age and diversification of
the angiosperms re-revisited. Am J Bot 97: 1296--1303.
doi:\href{http://dx.doi.org/10.3732/ajb.0900346}{10.3732/ajb.0900346}.

50. Wahlberg N, Rubinoff D (2011) Vagility across \emph{Vanessa} (Lepidoptera:
Nymphalidae): mobility in butterfly species does not inhibit the
formation and persistence of isolated sister taxa. Syst Entomol 36:
362--370.
doi:\href{http://dx.doi.org/10.1111/j.1365-3113.2010.00566.x}{10.1111/j.1365-3113.2010.00566.x}.

>>>>

We contrasted these results with those obtained from analysing the data in
the software BAMM {[}42{]}. We found 
that the best model (best configuration) estimated 2 diversification shifts in
our MCC tree (posterior probability = 0.79) for the Ithomiini
 and Satyrini. Bayes factor (BF) values strongly 
favored this model in comparison with a constant rate model (no diversification
shifts, BF $>$ 1,884).

@@

42. Rabosky DL (2014) Automatic Detection of Key Innovations, Rate Shifts, and
Diversity-Dependence on Phylogenetic Trees. PLoS ONE 9: e89543. doi:
\href{http://dx.doi.org/10.1371/journal.pone.0089543}{10.1371/journal.pone.0089543}.

43. Litman JR, Danforth BN, Eardley CD, Praz CJ (2011) Why do leafcutter
bees cut leaves? New insights into the early evolution of bees. P Roy
Soc B 278: 3593--3600.
doi:\href{http://dx.doi.org/10.1098/rspb.2011.0365}{10.1098/rspb.2011.0365}.

44. Ryberg M, Matheny PB (2012) Asynchronous origins of ectomycorrhizal
clades of Agaricales. P Roy Soc B 279: 2003--2011.
doi:\href{http://dx.doi.org/10.1098/rspb.2011.2428}{10.1098/rspb.2011.2428}.

45. Brown Jr. KS (1987) Chemistry at the Solanaceae/Ithomiinae
Interface. Ann Mo Bot Gard 74: 359--397.

46. Brower AVZ, Freitas AVL, Lee M-M, Silva-Brand{\~a}o KL, Whinnett A, et
al. (2006) Phylogenetic relationships among the Ithomiini (Lepidoptera:
Nymphalidae) inferred from one mitochondrial and two nuclear gene
regions. Syst Entomol 31: 288--301.
doi:\href{http://dx.doi.org/10.1111/j.1365-3113.2006.00321.x}{10.1111/j.1365-3113.2006.00321.x}.

47. {FitzJohn} RG, Maddison WP, Otto SP (2009) Estimating
trait-dependent speciation and extinction rates from incompletely
resolved phylogenies. Syst Biol 58: 595--611.
doi:\href{http://dx.doi.org/10.1093/sysbio/syp067}{10.1093/sysbio/syp067}.

48. Wheat CW, Vogel H, Wittstock U, Braby MB, Underwood D, et al. (2007)
The genetic basis of a plant-insect coevolutionary key innovation. P
Natl Acad Sci USA 104: 20427--20431.
doi:\href{http://dx.doi.org/10.1073/pnas.0706229104}{10.1073/pnas.0706229104}.

49. Li W, Schuler MA, Berenbaum MR (2003) Diversification of
furanocoumarin-metabolizing cytochrome P450 monooxygenases in two
papilionids: Specificity and substrate encounter rate. P Natl Acad Sci
USA 100: 14593--14598.
doi:\href{http://dx.doi.org/10.1073/pnas.1934643100}{10.1073/pnas.1934643100}.

50. Bell CD, Soltis DE, Soltis PS (2010) The age and diversification of
the angiosperms re-revisited. Am J Bot 97: 1296--1303.
doi:\href{http://dx.doi.org/10.3732/ajb.0900346}{10.3732/ajb.0900346}.

51. Wahlberg N, Rubinoff D (2011) Vagility across \emph{Vanessa} (Lepidoptera:
Nymphalidae): mobility in butterfly species does not inhibit the
formation and persistence of isolated sister taxa. Syst Entomol 36:
362--370.
doi:\href{http://dx.doi.org/10.1111/j.1365-3113.2010.00566.x}{10.1111/j.1365-3113.2010.00566.x}.
